### 2016-11-28 local-capability-machine.tex
changed iota^pwl to also allow permanent regions (to avoid issue in readCondition)

Standard regions for when writing locally is permitted:
\begin{align*}
  &\iota_{\start,\addrend}^{\var{pwl}} : \Views \fun \Regions\\
  &\iota_{\start,\addrend}^{\var{pwl}} \defeq \lambda \_ \ldotp(\temp,1,=,H^{\var{pwl}}) \\ \\
  &H^{\var{pwl}} : \States \fun (\Worwk \monnefun \UPred{\HeapSegments})\\
  &H^{\var{pwl}} \; (\start,\addrend) \; \hat{W} \defeq \left\{\npair{\hs} \middle|
    \begin{aligned}
      &\dom(\hs) = [\start,\addrend] \land \\
      &\forall \addr \in [\start,\addrend] \ldotp \npair[n-1]{\hs(\addr)} \in \stdvr(\xi_{\var{wk}}(\hat{W}))
    \end{aligned}
  \right\}
\end{align*}
Revoking all temporary regions:
\begin{align*}
  \revokeTemp{} & : \Worlds \fun \Worlds \\
  \revokeTemp{W} & \defeq \lambda r \ldotp 
                   \begin{cases}
                     \revoked            & \text{if }W(r) = (\temp,s,\phi,H) \\
                     W(r)                & \text{otherwise}
                   \end{cases}
\end{align*}
\newcommand{\wrev}[1]{\revokeTemp{#1}}

Standard regions for when write local is not allowed:
\begin{align*}
  &\iota_{\start,\addrend}^{\var{nwl}} : \Views \parfun \Regions \\
  &\iota_{\start,\addrend}^{\var{nwl}} \defeq \lambda v \ldotp
    \begin{cases}
      (v,1,=,H^{\var{nwl}}) & v \neq \revoked \\
      \bot & \text{otherwise}
\end{cases}
\\ \\
  &H^{\var{nwl}} : \States \fun (\Worstr \monnefun \UPred{\HeapSegments})\\
  &H^{\var{nwl}} \; (\start,\addrend) \;\hat{W} \defeq \left\{\npair{\hs} \middle|
    \begin{aligned}
      &\dom(\hs) = [\start,\addrend] \land \\
      &\forall \addr \in [\start,\addrend] \ldotp \\
      &\quad \npair[n-1]{\hs(\addr)} \in \stdvr(\revokeTemp{\xistr(\hat{W})})
    \end{aligned}
  \right\}
\end{align*}

>>>>

Standard regions for when writing locally is permitted:
\begin{align*}
  &\iota_{\start,\addrend}^{\var{pwl}} : \Views \fun \Regions\\
  &\iota_{\start,\addrend}^\pwl \defeq \lambda v \ldotp
    \begin{cases}
      (v,1,=,H^\pwl (\start,\addrend)) & v \neq \revoked \\
      \bot & \text{otherwise}
    \end{cases}
  &H^{\var{pwl}} : \Addrs^2 \fun \States \fun (\Worwk \monnefun \UPred{\HeapSegments})\\
  &H^{\var{pwl}} (\start,\addrend)\; s \; \hat{W} \defeq \left\{\npair{\hs} \middle|
    \begin{aligned}
      &\dom(\hs) = [\start,\addrend] \land \\
      &\forall \addr \in [\start,\addrend] \ldotp \npair[n-1]{\hs(\addr)} \in \stdvr(\xi_{\var{wk}}(\hat{W}))
    \end{aligned}
  \right\}
\end{align*}
Revoking all temporary regions:
\begin{align*}
  \revokeTemp{} & : \Worlds \fun \Worlds \\
  \revokeTemp{W} & \defeq \lambda r \ldotp 
                   \begin{cases}
                     \revoked            & \text{if }W(r) = (\temp,s,\phi,H) \\
                     W(r)                & \text{otherwise}
                   \end{cases}
\end{align*}
\newcommand{\wrev}[1]{\revokeTemp{#1}}

Standard regions for when write local is not allowed:
\begin{align*}
  &\iota_{\start,\addrend}^{\var{nwl}} : \Views \parfun \Regions \\
  &\iota_{\start,\addrend}^{\var{nwl}} \defeq \lambda v \ldotp
    \begin{cases}
      (v,1,=,H^{\var{nwl}} (start,\addrend)) & v \neq \revoked \\
      \bot & \text{otherwise}
\end{cases}
\\ \\
  &H^{\var{nwl}} : \Addrs^2 \fun \States \fun (\Worstr \monnefun \UPred{\HeapSegments})\\
  &H^{\var{nwl}} \; (\start,\addrend) \;\hat{W} \defeq \left\{\npair{\hs} \middle|
    \begin{aligned}
      &\dom(\hs) = [\start,\addrend] \land \\
      &\forall \addr \in [\start,\addrend] \ldotp \\
      &\quad \npair[n-1]{\hs(\addr)} \in \stdvr(\revokeTemp{\xistr(\hat{W})})
    \end{aligned}
  \right\}
\end{align*}
